%% frontmatter.tex
%%

\title{Secure, Anonymous Web-Hosting with Community-Driven Censorship}
\author{Scott Cunningham}
\degreemonth{April} % month final submission occurs.
\degreeyear{2014}
\degree{Bachelor of Arts}
\field{Computer Science}
\department{School of Computer Science and Statistics}
\advisor{Professor Stephen Barrett} % Category I added.

\maketitle

\chapter*{Declaration}

I hereby declare that this thesis is entirely my own work and that it
has not been submitted as an exercise for a degree at any other
university.

\begin{center}
    \vspace*{2in}

    \underline{\hspace*{3in}} \today

    Scott Cunningham

\end{center}

\chapter*{Permission to Lend}

I agree that the Library and other agents of
the College may lend or copy this thesis upon request.

\begin{center}
    \vspace*{2in}

    \underline{\hspace*{3in}} \today

    Scott Cunningham


\end{center}


\begin{abstract}
% limited to 1.5 pages, double-spaced (Registrar's Office guidelines).
% Also limited to 350 words. I claim $\mu \sim \omega^4$ is a single word.

Private, anonymous web-browsing is now more important than ever due to recent
allegations of mass internet surveillance by large government intelligence
agencies.
However, the solutions that currently exist in this problem space take extreme
anti-censorship positions,
and as a result are left largely un-moderated. While censorship is often
imposed by third parties and mis-used against the will of the users,
it is sometimes useful in removing legitimately harmful content from a network.
This project aims to design and implement an alternative private, anonymous
web-serving network which allows for censorship decided by members of the community.

\end{abstract}

\newpage
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents

% these are optional in the Jan 2000 Harvard thesis GSAS guide:
\listoffigures
%(Cut them for my personal thesis format).

% cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc

\begin{acknowledgments}

I would like to thank the following people for their help over the course of this project (in no particular order):
\begin{itemize}
	\item Prof. Stephen Barrett, who was a constant source of enthusiasm while supervising this project.
	\item Michael Clear, who was very helpful in giving me advice on cryptography.
	\item My girlfriend Izabela, who was patient and supportive throughout the project.
	\item My family for their support throughout my entire degree.
    \item Ian Hunter, who listened to my complaints and suggested ways to put them into writing.
\end{itemize}
\end{acknowledgments}


%ddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddd
\newpage

\startarabicpagination

%%% end

